Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression

### 2022-06-27 docs/rmd/presentation/slides.tex
done

@@

\leavevmode\vadjust pre{\hypertarget{ref-10.1007ux2f978-3-642-16493-4_19}{}}%
Fang, Y. and Li, J. (2010) {``A review of tournament selection in
genetic programming,''} in Cai, Z. et al. (eds.) \emph{Advances in
computation and intelligence}. Berlin, Heidelberg: Springer Berlin
Heidelberg, pp. 181--192.

\leavevmode\vadjust pre{\hypertarget{ref-6920034}{}}%
Helmuth, T., Spector, L. and Matheson, J. (2015) {``Solving
uncompromising problems with lexicase selection,''} \emph{IEEE
Transactions on Evolutionary Computation}, 19(5), pp. 630--643.
doi:\href{https://doi.org/10.1109/TEVC.2014.2362729}{10.1109/TEVC.2014.2362729}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-generalisation_in_gp}{}}%
Kushchu, I. (2002) {``An evaluation of EvolutionaryGeneralisation in
genetic programming,''} \emph{Artificial Intelligence Review - AIR}, 18,
pp. 3--14.
doi:\href{https://doi.org/10.1023/A:1016379201230}{10.1023/A:1016379201230}.

\leavevmode\vadjust pre{\hypertarget{ref-https:ux2fux2fdoi.orgux2f10.48550ux2farxiv.1709.05394}{}}%
La Cava, W. \emph{et al.} (2017) {``A probabilistic and multi-objective
analysis of lexicase selection and epsilon-lexicase selection.''} arXiv.
doi:\href{https://doi.org/10.48550/ARXIV.1709.05394}{10.48550/ARXIV.1709.05394}.

\leavevmode\vadjust pre{\hypertarget{ref-epsilon_lexicase_main}{}}%
La Cava, W., Spector, L. and Danai, K. (2016) {``Epsilon-lexicase
selection for regression,''} in \emph{Proceedings of the genetic and
evolutionary computation conference 2016}. New York, NY, USA:
Association for Computing Machinery (GECCO '16), pp. 741--748.
doi:\href{https://doi.org/10.1145/2908812.2908898}{10.1145/2908812.2908898}.

\leavevmode\vadjust pre{\hypertarget{ref-open_issues_gp}{}}%
O'Neill, M. \emph{et al.} (2010) {``Open issues in genetic
programming,''} \emph{Genetic Programming and Evolvable Machines}, 11,
pp. 339--363.
doi:\href{https://doi.org/10.1007/s10710-010-9113-2}{10.1007/s10710-010-9113-2}.

\leavevmode\vadjust pre{\hypertarget{ref-Orzechowski_2018}{}}%
Orzechowski, P., Cava, W.L. and Moore, J.H. (2018) {``Where are we
now?''} in \emph{Proceedings of the genetic and evolutionary computation
conference}. {ACM}.
doi:\href{https://doi.org/10.1145/3205455.3205539}{10.1145/3205455.3205539}.

\leavevmode\vadjust pre{\hypertarget{ref-bloat_overfitting_gp}{}}%
Silva, S. and Vanneschi, L. (2009) {``Operator equalisation, bloat and
overfitting: A study on human oral bioavailability prediction,''} in
\emph{Proceedings of the 11th Annual Genetic and Evolutionary
Computation Conference, GECCO-2009}, pp. 1115--1122.
doi:\href{https://doi.org/10.1145/1569901.1570051}{10.1145/1569901.1570051}.

\leavevmode\vadjust pre{\hypertarget{ref-wang_wagner_rondinelli_2019}{}}%
Wang, Y., Wagner, N. and Rondinelli, J.M. (2019) {``Symbolic regression
in materials science,''} \emph{MRS Communications}, 9(3), pp. 793--805.
doi:\href{https://doi.org/10.1557/mrc.2019.85}{10.1557/mrc.2019.85}.

>>>>

\begin{frame}{Github Repository}
\protect\hypertarget{github-repository}{}
Full paper, source code, results, plots and tables available at:

\textbf{\url{https://github.com/roman91DE/intelligent_information_systems_research_project/}}
\end{frame}

@@

\leavevmode\vadjust pre{\hypertarget{ref-10.1007ux2f978-3-642-16493-4_19}{}}%
Fang, Y. and Li, J. (2010) {``A review of tournament selection in
genetic programming,''} in Z. Cai et al. (eds.) \emph{Advances in
computation and intelligence}. Berlin, Heidelberg: Springer Berlin
Heidelberg, pp. 181--192.

\leavevmode\vadjust pre{\hypertarget{ref-6920034}{}}%
Helmuth, T., Spector, L. and Matheson, J. (2015) {``Solving
uncompromising problems with lexicase selection,''} \emph{IEEE
Transactions on Evolutionary Computation}, 19(5), pp. 630--643.
\url{https://doi.org/10.1109/TEVC.2014.2362729}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-generalisation_in_gp}{}}%
Kushchu, I. (2002) {``An evaluation of EvolutionaryGeneralisation in
genetic programming,''} \emph{Artificial Intelligence Review - AIR}, 18,
pp. 3--14. \url{https://doi.org/10.1023/A:1016379201230}.

\leavevmode\vadjust pre{\hypertarget{ref-https:ux2fux2fdoi.orgux2f10.48550ux2farxiv.1709.05394}{}}%
La Cava, W. \emph{et al.} (2017) {``A probabilistic and multi-objective
analysis of lexicase selection and epsilon-lexicase selection.''} arXiv.
\url{https://doi.org/10.48550/ARXIV.1709.05394}.

\leavevmode\vadjust pre{\hypertarget{ref-epsilon_lexicase_main}{}}%
La Cava, W., Spector, L. and Danai, K. (2016) {``Epsilon-lexicase
selection for regression,''} in \emph{Proceedings of the genetic and
evolutionary computation conference 2016}. New York, NY, USA:
Association for Computing Machinery (GECCO '16), pp. 741--748.
\url{https://doi.org/10.1145/2908812.2908898}.

\leavevmode\vadjust pre{\hypertarget{ref-open_issues_gp}{}}%
O'Neill, M. \emph{et al.} (2010) {``Open issues in genetic
programming,''} \emph{Genetic Programming and Evolvable Machines}, 11,
pp. 339--363. \url{https://doi.org/10.1007/s10710-010-9113-2}.

\leavevmode\vadjust pre{\hypertarget{ref-Orzechowski_2018}{}}%
Orzechowski, P., Cava, W.L. and Moore, J.H. (2018) {``Where are we
now?''} in \emph{Proceedings of the genetic and evolutionary computation
conference}. {ACM}. \url{https://doi.org/10.1145/3205455.3205539}.

\leavevmode\vadjust pre{\hypertarget{ref-bloat_overfitting_gp}{}}%
Silva, S. and Vanneschi, L. (2009) {``Operator equalisation, bloat and
overfitting: A study on human oral bioavailability prediction,''} in
\emph{Proceedings of the 11th Annual Genetic and Evolutionary
Computation Conference, GECCO-2009}, pp. 1115--1122.
\url{https://doi.org/10.1145/1569901.1570051}.

\leavevmode\vadjust pre{\hypertarget{ref-wang_wagner_rondinelli_2019}{}}%
Wang, Y., Wagner, N. and Rondinelli, J.M. (2019) {``Symbolic regression
in materials science,''} \emph{MRS Communications}, 9(3), pp. 793--805.
\url{https://doi.org/10.1557/mrc.2019.85}.
